\name: Deterministic and Coherent Implicits

### 2017-02-28 src/Conclusion.tex
Conclusion

This paper has presented $\ourlang$, the Calculus Of CoHerent ImplicitS, a new
calculus for implicit programming that improves upon the implicit calculus and
strikes a good balance between flexibility and coherence. In particular,
$\ourlang$ supports local scoping, overlapping instances, first-class
instances, and higher-order rules, while remaining type safe, coherent and
unambiguous.

In future work it would be interesting to integrate Genus's solution for the
global coherence problem~\cite{Zhang15LFO}.

>>>>

This paper presented $\ourlang$, the Calculus Of CoHerent ImplicitS, a new
calculus for implicit programming that improves upon the implicit calculus and
strikes a good balance between flexibility and coherence. In particular,
$\ourlang$ supports local scoping, overlapping rules, first-class
rules, and higher-order rules, while remaining type safe, coherent and
unambiguous.
Interesting future work includes integrating Genus's solution for the
instance coherence problem~\cite{Zhang15LFO} in $\ourlang$; and 
adding more features that show up 
in various IP mechanisms, such as \emph{associated types}~\cite{assoctypes,assoctypes2} and \emph{type
  families}~\cite{typefunc}.
